Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
consistent notation for coqdoc, slight reformulation on documentation

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

The \Hydras book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the \coq development, showing definitions (Fig.~\ref{fig:Hprime}), computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}), lemmas (Fig.~\ref{fig:Ex42E0}) and parts of  proof scripts (Fig.~\ref{fig:Ex42-schutte}). The order in which these references appear in the book is independent of the structure of our libraries, so we chose to maintain the book as a standalone document, separate from the \coq source code.  This  contrasts with the Coqdoc approach, where explanatory prose is embedded within \coq source files (a detailed discussion of various approaches to the documentation of \coq developments can be found  in \cite{alectryonpaper}).

@@

\item To generate the documentation of the project (book in PDF format and coqdoc HTML pages) by relying on the output of the coq\_makefile build.

>>>>

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

The \Hydras book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the \coq development, showing definitions (Fig.~\ref{fig:Hprime}), computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}), lemmas (Fig.~\ref{fig:Ex42E0}) and parts of  proof scripts (Fig.~\ref{fig:Ex42-schutte}). The order in which these references appear in the book is independent of the structure of our libraries, so we chose to maintain the book as a standalone document, separate from the \coq source code.  This contrasts with the \coqdoc approach, where explanatory prose is embedded within \coq source files (a detailed discussion of different approaches to documenting \coq developments can be found in \cite{alectryonpaper}).

@@

\item To generate the documentation of the project (book in PDF format and \coqdoc HTML pages) by relying on the output of the coq\_makefile build.
